\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-04-30 chapters/2_rel_work.tex
Small changes

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for joint segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,novotny2018semi,kulikov2018instance}. 
% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrent}.
%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}

@@

\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts. 
Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters; whereas the optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy. \TODO{Roman, Cocoons, Benjamin}
On the other hand, several segmentation pipelines use classical HC linkage criteria, e.g. average linkage \cite{liu2018affinity,lee2017superhuman} or median \cite{funke2018large}. The GALA algorithm in \cite{nunez2013machine,knowles2016rhoananet} features instead a linkage learned by a neural network.

\textbf{Clustering of signed graphs} is another important line of research with the goal of balancing a graph with both attractive and repulsive cues. Finding an optimally balanced clustering has a long history in the field of combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
The name \emph{correlation clustering} was coined by \cite{bansal2004correlation} that also showed its NP-hardness, while its connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problem instances of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger problems.
\TODO{Cannot-link constraints!}
% Missing: Funke proposals, discussion about cannot-link constraints!!!

>>>>

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for joint segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}. % Semi-convolutiona: \cite{novotny2018semi}
% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrent}.
%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}

@@

\textbf{Agglomerative graph clustering} has often been applied to instance segmentation \cite{ren2013image,liu2016image,salembier2000binary}, because of its efficiency as compared to other top-down approaches like graph cuts. 
Novel termination criteria and merging strategies have often been proposed: the agglomeration in \cite{malmberg2011generalized} deploys fixed sets of merge constraints; ultrametric contour maps \cite{arbelaez2011contour} combine an oriented watershed transform with an edge detector, so that superpixels are merged until the ultrametric distance exceeds a learned threshold; the popular graph-based method \cite{felzenszwalb2004efficient} stops the agglomeration when the merge costs exceed a measure of quality for the current clusters; whereas the optimization approach in \cite{kiran2014global} performs greedy merge decisions that minimize a certain energy. \TODO{Roman, Cocoons, Benjamin?}
On the other hand, several segmentation pipelines use classical HC linkage criteria, e.g. average linkage \cite{liu2018affinity,lee2017superhuman} or median \cite{funke2018large}. The GALA algorithm in \cite{nunez2013machine,knowles2016rhoananet} features instead a linkage learned by a neural network.

\textbf{Clustering of signed graphs} is another important line of research with the goal of balancing a graph with both attractive and repulsive cues. Finding an optimally balanced clustering has a long history in the field of combinatorial optimization \cite{grotschel1989cutting,grotschel1990facets,chopra1993partition}. %and can be done without the need to specify a termination criterion. 
The name \emph{correlation clustering} was coined by \cite{bansal2004correlation} that also showed its NP-hardness, while its connection with graph multicuts was made by \cite{demaine2006correlation}. Modern integer linear programming solvers can tackle problem instances of considerable size \cite{andres2012globally}, but accurate approximations \cite{pape2017solving,beier2016efficient,yarkony2012fast}, greedy heuristic algorithms \cite{levinkov2017comparative,wolf2018mutex,keuper2015efficient,kardoostsolving} and persistence criteria \cite{lange2018partial,lange2018combinatorial} have been proposed for even larger problems.
\TODO{Cannot-link constraints?}
% Missing: Funke proposals, discussion about cannot-link constraints!!!
